%-------------------------
% ATS-Friendly Resume in LaTeX
% Author : Rasheeque Ahammed Rahim
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Use Roboto font for better readability and space efficiency
\usepackage[sfdefault]{roboto}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins - tighter for one page
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING - CENTERED----------
\begin{center}
    \textbf{\Huge \scshape Rasheeque Ahammed Rahim} \\ \vspace{1pt}
    \small AI \& ML Development Engineer \\ \vspace{3pt}
    \small \href{mailto:rasheequeraheem78@gmail.com}{rasheequeraheem78@gmail.com} $|$ 
    +91 9207252943 $|$ 
    \href{https://www.linkedin.com/in/rasheeque-ahammed-raheem-aa777325a}{LinkedIn} $|$
    \href{https://github.com/Rasheequeahammed}{GitHub} $|$
    \href{https://rasheequeahammed.github.io/Rasheeque-PortFolio/}{Portfolio}
\end{center}
\vspace{-5pt}

%-----------SUMMARY-----------
\section{Professional Summary}
  \small{Motivated AI/ML Development Engineer with hands-on experience in building scalable machine learning and deep learning solutions. Proficient in Python and frameworks like TensorFlow, PyTorch, and scikit-learn. Demonstrated success in NLP, computer vision, and real-time ML applications. Strong analytical mindset and collaborative approach, eager to contribute to innovative AI-driven products.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{ML/AI:} TensorFlow, PyTorch, scikit-learn, Keras, XGBoost, YOLO, BERT, LLaMA, NLP, Computer Vision, Deep Learning \\
     \textbf{Programming:} Python (Pandas, NumPy, OpenCV, Transformers), R, SQL \\
     \textbf{Tools \& Cloud:} Git, Docker, Streamlit, GCP, BigQuery, Docker, Tableau, Power BI, MySQL \\
     \textbf{Specializations:} Real-time Video Analytics, Spatial AI, Object Detection, Retail Automation, Generative Design \\ \textbf{Certifications:} IBM Gen AI, GCP Foundations, AI/DL (360DigiTMG)
    }}
 \end{itemize}
 \vspace{-8pt}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI ML Development Engineer}{May 2025 -- Present}
      {Think Neural AI}{Remote}
      \resumeItemListStart
        \resumeItem{Develop and deploy ML pipelines for real-time video analytics and spatial AI serving major retail clients (Lenskart, MR.DIY), achieving 96\%+ accuracy in object detection and processing 1000+ hours of video data monthly.}
        \resumeItem{Engineer YOLO-based computer vision models for automated object detection, behavioral analysis, boundary detection, and anomaly recognition in retail environments.}
        \resumeItem{Build scalable generative design algorithms to automate CAD layout generation from 3D scan data, reducing design time by 80\% and improving store rollout efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Scientist Intern}{March 2024 -- October 2024}
      {Innodatatics}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Built and optimized ML models using TensorFlow/scikit-learn, improving accuracy by 15\% through hyperparameter tuning, feature engineering, and cross-validation on datasets with 100K+ records.}
        \resumeItem{Deployed AI solutions reducing operational costs by \$1M+, including YOLO-based inventory counting (96\% accuracy); collaborated on NLP (DistilBERT) and CV projects for retail/healthcare.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  \vspace{-3pt}

%-----------PROJECTS-----------
\section{Key Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{SpaceZap.AI - AI-Driven Retail Site Survey \& Design Automation}}{May 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Engineered end-to-end ML pipelines to automate retail site surveys and 3D fit-out designs using computer vision models for boundary detection and spatial analysis across 50+ retail locations.}
            \resumeItem{Automated LiDAR/3D scan conversion to CAD-ready layouts with generative design logic. \textit{Tech: PyTorch, OpenCV, CAD Automation, LiDAR}}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Sakshi.AI - Real-Time Video Analytics \& Surveillance Platform}}{May 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed real-time video analytics platform for retail/industrial surveillance monitoring 100+ camera feeds with vision models for object detection, behavioral analysis, and anomaly recognition.}
            \resumeItem{Implemented scalable video processing workflows providing actionable insights and alerts. \textit{Tech: TensorFlow, YOLO, OpenCV, Stream Processing}}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Emotion Detection \& Adaptive Response Chatbot}}{November 2024 -- January 2025}
          \resumeItemListStart
            \resumeItem{Built emotion-aware chatbot using DistilBERT \& LLaMA on GoEmotions dataset (28 emotions), achieving 92\% accuracy; deployed on Hugging Face with Streamlit UI handling 500+ interactions. \textit{Tech: Transformers, NLP, Fine-tuning}}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
    \vspace{-3pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Masters in Computer Application (MCA) - AI Specialization}{2023 -- 2025}
      {Amrita Vishwa Vidyapeetham (Amrita AHEAD)}{}
    \resumeSubheading
      {Bachelor of Science in Computer Science}{2020 -- 2023}
      {College of Applied Science Koothuparamba, Kannur, India}{}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
