%-------------------------
% Software Developer Resume - Zoho Focused
% Author : Rasheeque Ahammed Rahim
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Use Roboto font for better readability
\usepackage[sfdefault]{roboto}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins - tighter for one page
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING - CENTERED----------
\begin{center}
    \textbf{\Huge \scshape Rasheeque Ahammed Rahim} \\ \vspace{1pt}
    \small Software Developer \\ \vspace{3pt}
    \small \href{mailto:rasheequeraheem78@gmail.com}{rasheequeraheem78@gmail.com} $|$ 
    +91 9207252943 $|$ 
    \href{https://www.linkedin.com/in/rasheeque-ahammed-raheem-aa777325a}{LinkedIn} $|$
    \href{https://github.com/Rasheequeahammed}{GitHub} $|$
    \href{https://rasheequeahammed.github.io/Rasheeque-PortFolio/}{Portfolio}
\end{center}
\vspace{-5pt}

%-----------SUMMARY-----------
\section{Professional Summary}
  \small{Versatile Software Developer with expertise in full-stack development and AI/ML integration. Proficient in Python, JavaScript, and modern frameworks (Django, Node.js, React, FastAPI). Currently handling multiple projects at a growing startup, demonstrating clean code practices, system design, and performance optimization. Strong foundation in data structures, algorithms, and emerging AI technologies.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming:} Python, JavaScript, Java, C++, C, SQL $|$ \textbf{Web:} React, Node.js, Django, FastAPI, REST APIs, HTML/CSS \\
     \textbf{Databases:} PostgreSQL, MySQL, MongoDB $|$ \textbf{Tools:} Git, Docker, GCP, VS Code \\
     \textbf{AI/ML:} TensorFlow, PyTorch, scikit-learn, Computer Vision, NLP $|$ \textbf{Core:} DSA, OOP, System Design, Performance Optimization
    }}
 \end{itemize}
 \vspace{-8pt}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{May 2025 -- Present}
      {Think Neural AI}{Remote}
      \resumeItemListStart
        \resumeItem{Design and develop scalable full-stack applications handling multiple concurrent projects across software development lifecycle.}
        \resumeItem{Build high-performance APIs and microservices using Python (Django/FastAPI) and Node.js, integrating AI/ML capabilities for intelligent features.}
        \resumeItem{Optimize application performance reducing response times by 80\% through efficient algorithms and caching strategies.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer Intern}{March 2024 -- October 2024}
      {Innodatatics}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed production-ready solutions improving efficiency by 15\% through code optimization and best practices.}
        \resumeItem{Collaborated on full-stack projects in Agile environment, delivering features integrating Python, JavaScript, and SQL.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  \vspace{-3pt}

%-----------PROJECTS-----------
\section{Key Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Retail Management System - Full Stack POS Application}}{Personal Project}
          \resumeItemListStart
            \resumeItem{Implemented RESTful APIs, user authentication, real-time data synchronization, and integrated business intelligence dashboard for retail insights.}
            \resumeItem{Built comprehensive POS with FastAPI backend and React frontend featuring inventory management, multi-store support, and AI-powered analytics for sales forecasting. \textit{Tech: Python, FastAPI, React, PostgreSQL, REST APIs}}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{SpaceZap.AI - Spatial Design Automation}}{Think Neural AI}
          \resumeItemListStart
            \resumeItem{Engineered end-to-end ML pipelines to automate retail site surveys and 3D fit-out designs using computer vision models for boundary detection and spatial analysis across 50+ retail locations.}
            \resumeItem{Engineered scalable system automating CAD layout generation using ML algorithms, reducing processing time by 80\% for 50+ locations. \textit{Tech: Python, Django, PostgreSQL, Algorithm Optimization}}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Sakshi.AI - Real-Time Analytics Platform}}{Think Neural AI}
          \resumeItemListStart
            \resumeItem{Developed high-performance backend for real-time data processing monitoring 100+ concurrent streams with AI-based analytics. \textit{Tech: Python, FastAPI, PostgreSQL, WebSockets}}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
    \vspace{-3pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Masters in Computer Application (MCA)}{2023 -- 2025}
      {Amrita Vishwa Vidyapeetham (Amrita AHEAD) - Grade A}{}
    \resumeSubheading
      {Bachelor of Science in Computer Science}{2020 -- 2023}
      {College of Applied Science Koothuparamba, Kannur, India - Grade A}{}
  \resumeSubHeadingListEnd
  \vspace{-5pt}

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Google Cloud Computing Foundations $|$ Postgraduate Diploma in AI (SUNY, USA) $|$ IBM Generative AI Engineering
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
